---
author: "Maggie Klope"
title: "r-reticulate"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Reticulate

Reticulate is an R package that allows for the interface between R and Python.  It lets you call Python within R and translate between R and Python.

Upon the first install, reticulate will prompt you to download minconda in the console.  Enter Y to approve, or else you will have to use the install_miniconda() function.

Useful Links:

https://rstudio.github.io/reticulate/

https://rstudio.com/resources/cheatsheets/


```{r, include=FALSE}

#cinstall.packages("reticulate")
library(reticulate)

```

### Python Versions

Reticulate binds to a local instance of Python when you either implicitly or when you call the import() function, but you can suggest your own Python instance/environment.  To unbind, you must restart R.

```{r}
# py_config() for information about the version on Python you are using and a list of other version on your system:
py_config()

# To find the default version of Python Reticulate will use
Sys.which("python")

# Or specify a version
# use_python("usf/local/bin/python")

# or use a version in a virtual environment:
# list available virtual environments
virtualenv_list()

# use_virualenv("environ")

# Can create new virtual environment
# virtualenv_create("r-reticulate")

```

### Installing & importing python packages

- method depends on environment (virtual environment, conda, etc)
  - py_install() if using python binary
  - virtualenv_install() if using virtual environment
  - conda_install() if using conda environment
- can also use terminal:
  1) navigate into your bin or virtual environment
  2) use pip install.  Ex: "pip install SciPy"

```{r}
# install pandas
# conda_install(envname = "/home/klope/.local/share/r-miniconda", "pandas")

# import pandas (it will be automatically discovered in "r-miniconda")
pd <- import("pandas")

# how to check if a package is available for you to use:
py_module_available("pandas")

```

### Testing python code in console

Can use repl_python() in console, hit control+enter and run Python and view the results.
Type Python code at the >>> and hit return to run
Type "exit" to end

### Using a .py Python file in R studio

- File -> New File -> Python Script

### Using Python in R Markdown

To insert a Python code chunk: Insert -> Python.

```{python}

list = [11,22,33,44,55,66]

print(list)

```

#### Communicating between Python and R

You can communicate between Python and R (Rstudio v.2.1 and newer).  

First, we will upload the iris dataset into R:

```{r}

flowers <-  iris

```

We can reference our R objects by preceding their name with "r."

```{python}

import pandas

flowers_py = r.flowers

flowers_py_groups = flowers_py.groupby("Species")

group_means = flowers_py_groups.mean()

```
 
We can access our Python objects using py followed by $

```{r}

plot(py$group_means)

```

### Converting between Python and R

with r_to_py() and py_to_r()

### Reading in python scripts

```{r}

source_python('add.py')
add(5, 10)

```


