---
author: "Maggie Klope"
title: "r-reticulate"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}

#install.packages("reticulate")
library(reticulate)

```

### Python Versions

Reticulate binds to a local instance of Python when you either implicitly or when you call the import() function, but you can suggest your own Python instance/environment

To unbind, you must restart R.
```{r}
#py_config() for information about the version on Python you are using and a list of other version on your system:
py_config()

#To find the default vertion of Python
Sys.which("python")

#Or specify a version
use_python("usf/local/bin/python")

#or use a version in a virutal environment:
use_virualenv("environ")

```

### Using a virtual environment:

```{r}
#list available virtual environments
virtualenv_list()

#Create new virtual environment
virtualenv_create("r-reticulate")

```

### Installing python packages
- method depends on environment
- can also use terminal:
  1) nativage into your bin or virtual enviornment
  2) use pip install.  Ex: "pip install SciPy"

```{r}
#py_install()
#py_install("pandas")

#install within a virtual environment:
#virtualenv_install("r-reticulate", "scipy")

```

### Importing Python Modules
use the import() function to import a Python module in R
```{r}
pandas <- import("pandas")

# install SciPy into a virtual environment
virtualenv_install("r-reticulate", "scipy")

#access functions of the module with #
# pandas$date_range

# if you have a package installed on multiple instances of pytho, you can use use_virtualenv() to ensure that a specific virutalenv is utlized by reticulate:
use_virtualenv("r-reticulate")

# import SciPy (will use "r-reticulate" as per call to use_virtualenv)
scipy <- import("scipy")

```

### Testing python code in console
Can use repl_python() in cosole, hit control+enter and run Python and view the results.
Type Python code at the >>> and hit return to run
Type "exit" to end

### Using a .py Python file in R studio
- File -> New File -> Python Script

### Problem-sovling with shell

```{r}


```

